Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2023-06-16 analysis/paper_draft4.Rmd
added paragraph on incompatibility to discussion.

Since _Batson v. Kentucky_ [-@batson1986], a party violates the Equal Protection Clause of the United States Constitution by using peremptory challenges if motivated by the prospective jurors' race, ethnicity, sex, or certain other cognizable classes. The party bringing a _Batson_ challenge bears the burden of proving such illegal bias is more likely than not to be true [@LaFave2022, $\S$ 22.3(d)].

@@

>>>>

Since _Batson v. Kentucky_ [-@batson1986], a party violates the Equal Protection Clause of the United States Constitution by using peremptory challenges if motivated by the prospective jurors' race, ethnicity, sex, or certain other cognizable classes. The party bringing a _Batson_ challenge bears the burden of proving such illegal bias is more likely than not to be true [@LaFave2022, $\S$ 22.3(d)]. For clarity, we note that here, and throughout this paper, we are referring to bias as prejudice against selecting members of cognizable classes to serve on a jury and not bias in a statistical sense, or bias in a parameter. Rather, bias is the parameter we are trying to estimate. [EDITME]

@@

[EDITME]Our simulations demonstrate that when bias is high in either the historical _or_ current data, bias can be detected, especially when $\alpha$ is close to 1. For example, when $b_{curr}$ = 0, $b_{hist}$ = 3, and alpha = 1 our simulation bias detection rate is 1, when there are two or three historical trials (Fig X). In a scenario where we are using real data, and the true values of alpha are not known, these represent cases of extreme incompatibility, and should be detectible through sentivity checking of the value of $\alpha$. For instance, when the value of $\alpha$ is set to 0.1, the bias detection rate goes down to 0.02 for both the two and three historical data set simulations. Such sensitivity to the value of $\alpha$ is indicative of incompatibility between current and historical data.
